---
title: "NYCFlights: Arrival Delay Logictic Model"
author: "[Your Name]"
date: "[Today's Date]"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Logsitic and Inverse Logistic Transformation 

- Write an R function for the logistic function. The function should accept a `numeric` vector with values `[-Inf,Inf]` and produce a numeric vector in the the range `[0,1]`.

- Plot the logistic function from  `[-10,10]`

- Write a R function for the inverse logistic function. The function should accept a `numeric` vector with values `[0,1]` and prodcuce a numeric vector in the range `[-Inf,Inf]`

- Plot the Inverse Logistic function from `[0,1]`


**Hint:** For plotting curves see `?graphics::curve` or `?ggplot2::stat_function`

```{r "Logistic and Inverse Logistic" }
logistic <- function(x) {
  c(exp(x)/(1+exp(x)))
  
}

plot(c(-10,10),logistic(c(-10,10)),main="Scatterplot for Logistic function", 
     xlab="Vector", ylab="Logistic Function", pch=20)

curve(logistic,from=-100,to=100)


inverse <- function(y) {
  c(log(y/(1-y)))
}

plot(c(0.3,0.9),inverse(c(0.3,0.9)),main="Scatterplot for Inverse Logistic function", 
     xlab="Vector", ylab="Inverse Logistic Function", pch=20)

curve(inverse,from=0,to=1)


```


# NYCFlights Model

Using the rectangular data that you created from assignment and following the *Predicting Medical Expenses* example from the text (*MLwR*), create a model for arr_delay >= 15 minutes. Follow *MLwR* structure   for building a model. Describe/Explain each of the steps and show all work in codeblocks below.

KNIT YOUR DOCUMENT AS *HTML* AND SUBMIT IT AND THE `Rmd` file.   

## Step 1: Collect Data 

```{r "Step 1: Collect Data" }

Data <- copy(YX)

```

## Step 2: Explore and Prep The Data


One of the things not done in the MLwR text is a pairwise comparison between the response and each of the predictors. Make sure to do this; this is often very illustrative of the relationship between that predictor and the response. This can be done with `pairs` or `psych::panel.pairs`


```{r "Step 2: Explore and Prep The Data" }
##Response
Data[,delayed := arr_delay >= 15]
- Data$delayed
qplot(Data$delayed,colour="green")
boxplot(Data$delayed)


 Data <- Data[ delayed >= quantile(delayed,0.01,na.rm=TRUE) &  
           delayed <= quantile(delayed,0.96,na.rm=TRUE) ]

```

## Step 3:  Train The Model

```{r "Step 3: Train The Model" }
# Naive model
naive <- mean(Data$delayed)

form <- delayed ~ dep_delay
fit1 <- glm( form, Data %>% sample_n(1000),family=binomial )

form <- delayed ~ faa + dep_delay + lat +lon +alt + dst + arr_time + carrier + distance + minute + year + day + month + air_time + wind_gust + precip

fit2 <- glm( form , Data %>% sample_n(1e5),family=binomial )

?sample_n


```

## Step 4: Evaluate Performance

Think about some of the tools that you have for evaluating performance.  Choose one and articulate why you have chosen it.

```{r "Step 4: Evaluate Performance" }

data_test <- Data %>% tail(1e5)
predicted_prob <- predict(fit2,data_test,type="response")
head(predicted_prob)
install.packages("gmodels")
library("gmodels")
CrossTable(Data$dep_delay,Data$delayed) 

```

 
## Step 5: Improve Performance 

Show some steps for improving model performance.

```{r "Step 5: Improve Performance" }
install.packages("caret")
library("caret")
modelLookup("fit2")

```


# Question:

Is this a good model?  (Write your answer here.)


# PART B:

Your model should be good at explaining tardiness. Now, assume that your job is to predict arrival delays a month in advance. You can no longer use all the features in your model. Retrain your model using only features that will be *known* only a month in advance of the departure time.  Show all steps as above.

str(Data)
#Step 1: Collect Data
str(Data)

## Step 2: Explore and Prep The Data
## Predictors

This is reasonable list of variables that can be used 

- fligths
  - month             **
  - dep_delay (?)     
  - carrier / flight  *
  - origin            *
  - dest              *
  - air_time          **
  - distance          **  (can make up time in the air)
  - air time / hour / minute not known at end of flight
  
- planes
  - year              ** 
  - type              **
  - manufacture
  - engines          (not much variation)
  - seats
  - engine           **
  - speed            (Too many NAs decrease the performance of the model)

- weather 
  - temp             
  - dewp
  - wind_dir         
  - wind_gust         
  - precip           
  - pressure         
  - visib            
  
- airports (origin and dest)
  - faa or name
  - lat             ** dest(only)
  - lon             ** dest(only)
  - alt              
  



#The independent factors to predict arr_delay forone month in the future would be
form <- faa + sched_dep_time + sched_arr_time + distancelat +lon +year*month*day

## Step 3:  Train The Model
fit <- glm( form , Data %>% sample_n(1e5) )
library(MASS)
fit.step <- stepAIC(fit, scope=list(upper=. ~ ., lower = . ~ 1 ) )

## Step 4: Evaluate Performance" 

fit %>% resid %>% .^2 %>% mean %>% sqrt 




