---
title: "Classification Metrics"
author: "Christopher Brown"
date: 
output: html_document
---

The German Credit Data (data/german_credit); 

1. Read in the German Credit Data

getwd()
setwd("C:/Users/Venkatesh/Documents/Machine Learning/tmp/CSX460/data")
credit_info <- read.csv("german_credit.csv", stringsAsFactors = FALSE)

2. Partition the model into Test and Training Sets using only `base::sample` 

credit_train_sample <- credit_info[101:1000,]
credit_train_sample
credit_test_sample <- credit_info[1:100,]
credit_test_sample

rownames(credit_test_sample) <- c()

3. Train a model for `Creditability` 

naivefit <- median(credit_info$Creditability)
naivefit


form <- Creditability ~ .
fit <- glm(form,credit_train_sample,family=binomial)

summary(fit)

improvedform <- Creditability ~ Account.Balance + Duration.of.Credit..month. + Payment.Status.of.Previous.Credit + Value.Savings.Stocks + Length.of.current.employment + Instalment.per.cent + Sex...Marital.Status

improvedfit <- glm(improvedform,credit_train_sample,family=binomial)
summary(improvedfit)


4. Knit the document and submit both the this file Rmd and html files.

knitr::opts_chunk$set(echo = TRUE)

Show All Work! 

```{r}


```


Using the `predict` function and `test` data, write functions to calculate and 
calculate: 
?predict
predicted_prob <- predict(improvedfit, credit_test_sample,type="response")


head(predicted_prob)

credit_wrothy <- predicted_prob
credit_risk <- 1-predicted_prob

credit_results <- data.frame(credit_wrothy,credit_risk)
credit_results$predicted_result <- ifelse(credit_results$credit_wrothy >= 0.5, 1, 0)
credit_results$actual_result <- credit_test_sample$Creditability

credit_results

table(credit_results$actual_result,credit_results$predicted_result)

install.packages("gmodels")
library(gmodels)
CrossTable(credit_results$actual_result,credit_results$predicted_result)

TN <- 3
TP <- 89
FN <- 7
FP <- 1

total <- TN + TP + FN + FP

Cross

* Misclassification Rate
(FP + FN)/total

* Prevalence 
(FN + TP)/total

* Accuracy
(TP + TN)/total

* True Positive Rate 
(TP)/(FN + TP)

* False Positive Rate
FP/(FP + TN) 

* True Negative Rate  
TN/(TN + FP)

* False Negative Rate 
FN/(TN + FP)

* Sensitivity
(TP)/(FN + TP)

* Specificity 
TN/(TN + FP)

* Recall 
TP/(TP + FN)


* Precision
TP/(TP + FP)

install.packages('e1071', dependencies=TRUE)
library(caret)
confusionMatrix(credit_results$predicted_result,credit_results$actual_result,positive="1")


```{r, echo=FALSE}


```
