---
title: "Classification Metrics"
author: "Christopher Brown"
date: 
output: html_document
---

The German Credit Data (data/german_credit); 

1. Read in the German Credit Data

getwd()
setwd("C:/Users/Venkatesh/Documents/Machine Learning/tmp/CSX460/data")
credit_info <- read.csv("german_credit.csv", stringsAsFactors = FALSE)

2. Partition the model into Test and Training Sets using only `base::sample` 

credit_train_sample <- credit_info[1:900,]
credit_train_sample
credit_test_sample <- credit_info[901:1000,]
credit_test_sample

rownames(credit_test_sample) <- c()

3. Train a model for `Creditability` 

naivefit <- median(credit_info$Creditability)
naivefit


form <- Creditability ~ .
fit <- glm(form,credit_train_sample,family=binomial)

summary(fit)

improvedform <- Creditability ~ Account.Balance + Duration.of.Credit..month. + Payment.Status.of.Previous.Credit + Value.Savings.Stocks + Length.of.current.employment + Instalment.per.cent + Sex...Marital.Status
improvedfit <- glm(improvedform,credit_train_sample,family=binomial)
summary(improvedfit)


4. Knit the document and submit both the this file Rmd and html files.

knitr::opts_chunk$set(echo = TRUE)

Show All Work! 

```{r}


```


Using the `predict` function and `test` data, write functions to calculate and 
calculate: 
?predict
predicted_prob <- predict(improvedfit, credit_test_sample,type="response")
head(predicted_prob)

* Misclassification Rate
* Prevalence 
* Accuracy
* Accuracy
* Error Rate / Misclassification Rate
* True Positive Rate  
* False Positive Rate
* True Negative Rate  
* False Negative Rate 
* Sensitivity 
* Specificity 
* Recall 
* Precision

```{r, echo=FALSE}


```
